---
title: "Untitled"
author: "NLB"
date: "4/28/2021"
output: html_document
---


```{r}
#install.packages("rmarkdown")
#install.packages('knitr') 
#install.packages("quanteda")
#install.packages("tidyverse")
#install.packages("readr")
#install.packages("syuzhet")
#install.packages("dplyr")
#install.packages("qcc")
#install.packages("ggplot2")
#install.packages("reshape2")
library(rmarkdown)
library(knitr)
library(quanteda)
library(tidyverse)
library(readr)
library(syuzhet)
library(dplyr)
library(qcc)
library(ggplot2)
library(reshape2)
```


```{r}
#setwd("~/Desktop/MIIC/data-GoogleAnalytics/bis")
 
#data1 <- read.csv(data1)
```


# REVISION----

# see my dataset


# summarize the content 



# Subset my dataset by columns and subsets (editorial vs. transactional)
```{r}
table(data1$`Type de page`)
edito <- data1[data1$`Type de page`=="Editorial",]
transac <- data1[data1$`Type de page`=="Transactionnel",]
```


# Get the number of tokens in {quanteda} for the English column
```{r}
library(quanteda)
mycorpus <- corpus(data1$`Conteu (en)`)
mydfm <- dfm(mycorpus)
ntok <- ntoken(mydfm)

data1$ntoken_en <- ntoken(dfm(corpus(data1$`Conteu (en)`)))
``
# Boxplot number of tokens (French)
```{r}
boxplotnumberoftokens <- boxplot(data1$notoken_fr,main ="Boxplot Number of Tokens")
```


# Get the number of tokens in {quanteda} for the French column
```{r}
data1$notoken_fr <- ntoken(dfm(corpus(data1$Contenu)))
```


# Get the number of types in French and English
```{r}
data1$ntype_fr <- ntype(dfm(corpus(data1$Contenu)))
data1$ntype_en <- ntype(dfm(corpus(data1$`Conteu (en)`)))
```

# Boxplot number of tokens (French)
```{r}
boxplotnumberoftokens <- boxplot(data1$notoken_fr,main ="Boxplot Number of Tokens")
```

# Compare number of tokens for editorial vs transactional pages 
```{r}
boxplotnumberoftokensedito <- boxplot(edito$notoken_fr,main ="Boxplot Number of Tokens for Editorial Pages")
```
```{r}
boxplotnumberoftokenstransac <- boxplot(transac$notoken_fr,main ="Boxplot Number of Tokens for Transactional Pages")
```


# TOP 10 pages 
```{r}
ordered_bouncing <- arrange(data1,desc(`Taux de rebond (%)`))
top10_bouncing <- head(ordered_bouncing,10)

ordered_visits <- arrange(data1,desc(`Nombre de visites`))
top10_visits <- head(ordered_visits,10)

ordered_timespent <- arrange(data1,desc(`Temps moyen passé sur la page (s)`))
top10_timespent <- head(ordered_timespent,10)

```


# FLOP 10 
```{r}
class(data1$`Nombre de visites`)

ordered_visits <- arrange(data1,desc(`Nombre de visites`))
max <- head(ordered_visits,1)
print(max$Page)
flop10visits <-tail(ordered_visits,10)
```


# TOP 5 number of visits for transactional pages
```{r}
ordered_visits <- arrange(transac,desc(`Nombre de visites`))
top5_visits <- head(ordered_visits,5)
```


# Pareto chart for the number of visits (whole dataset)

```{r, Pareto chart}
library(qcc)
pareto.chart(data1$`Nombre de visites` , xlab = "pages", las=1, ylab = "Number of visits", main="Pareto Chart of Number of visits ")

```


